---
title: "linear model from Web"
author: "Amber Walker"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged. Then form three regression models; Model1 is SIMS\~ARM, Model2 is SIMS\~GRIP, and Model3 is SIMS\~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94 for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link.

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM\~ARMS






### scatterplot

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

These results show that there is a fair amount of relationship between Sims and Arm strength.

### Inferential (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
Adjusted R square and multiple R square compared is that we always look at the adjusted R square numbers. As you put more in your  model, the adjusted Rsquared will go up.

#### Predict at target point


```{r}
mydata<- data.frame(GRIP=88,ARM= 104)
predict.lm(model.1, mydata, interval = "prediction")
```
The value it predicted was a 1.58 in change but it could go from a a negative .863 to a positive 4.02 in change.
 

#### scatterplot with model fit

```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```


## Model 2 SIM\~GRIP


### Now add in scatterplot

```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  labs(title = "SIMS and GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip
```

### Numerical results

```{r}
cor(SIMS~GRIP,data=data)
```

These results show that there is a fair amount of relationship between Sims and Arm strength.
Sims verses ARM has a bigger number for the correlation. So it is mote correlated to ARM than it is to GRIP 

### Inferential (Build model.2)

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

The results show that the SIMS verses R model is better that the SIMS verse GRIP model.

#### predict model.2 at target point

```{r}
predict.lm(model.2, mydata, interval ="prediction")
```
The interval goes from -3.38 to positive 1.766

#### now add the model fit to our plot for model.2


```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip

```


## Model 3 SIM\~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
When you run SIMS with both of them you get a higher coorelation then when you just run SIMS with ARM and SIMS with GRIP.


### Inferential (Build 2-dimentional model.3)

#### predict model.3 at target point

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

### Model.2 vs Model.3

## Informally compare Model.1 with model.2
